---
title: "Billboard 100 Presentation"
format: html
editor: visual
---

```{r}
library(dplyr)
library(ggplot2)
```

# Billboard 100 Analysis

## Read-in Data

The data needs to be created before running this code! The script to create the data is in the `billboard_100.R` file which can be run easily after you have installed all of the project dependencies! After you have created the data, you can read it in using the following code:

```{r}
top_billboard_ranking <- readRDS("top_billboard_ranking.rds")
```

If you have created the data, then try to render this document with the Render button in RStudio to see the analysis!

## Longest Charting Songs

```{r}
top_billboard_ranking %>%
  arrange(desc(weeks_in_top_100)) %>%
  head(10)
```

## Plot Most Popular Songs by Duration in Top 100

```{r}
top_billboard_ranking %>%
  ggplot(aes(x = weeks_in_top_100)) +
  geom_histogram(binwidth = 1) +
  labs(title = "Distribution of Weeks in Top 100",
       x = "Weeks in Top 100",
       y = "Count")
```
